\Large \bf \projtitle

### 2015-05-08 doc/paper/paper.tex
Fix

\section{Introduction}
It is common for personal blogs and other small websites to gain sudden attention
on large, high-traffic websites such as reddit. Since these websites usually
experience much smaller traffic loads, the hardware devoted to hosting them
is typically not powerful enough to cope with this large influx of content requests.
These sudden, unexpected bursts of traffic often result in websites loading at
extremely slow speeds, or not loading at all, and is colloquially known as the
``reddit hug of death'' or the ``reddit effect.'' \\

Typical means for dealing with this situation involve utilizing Content
Delivery Networks (CDNs), but these are expensive, especially for websites
which only experience such high loads on an occasional basis. An ideal solution
would be a lightweight means to mimic the benefits of an ordinary CDN, which is
typically backed by a robust network of machines. \\

In this paper, we present \zbf, a peer-to-peer CDN. \zbf provides an easy way
for developers to distribute content to clients via a peer-to-peer network,
rather than directly from the central server that hosts the content. \zbf
is comprised of a server-side component and a client-side component. The
centralized, server-side component both tracks resource propagation metadata
and acts as an assist for opening peer-to-peer data channel connections. The
lightweight client-side component requests resources from peers and distributes
resources in response to peer requests. \\

\zbf's design is based on the BitTorrent protocol~\cite{cohen:bittorrent}, by which
clients requesting content attempt to receive chunks of data from other
clients, rather than retrieving the entire file from a central server. As
with BitTorrent trackers, any developer could host their own tracker and service
it to connect peers requesting a resource with peers distributing the resource. \\

The \zbf client-side code runs purely in the browser, and is completely transparent
to the user. The user does not have to install any application on their
computer to obtain desired resources peer-to-peer. As a result, the \zbf client
code only runs when a user is currently visiting the website, therefore adding
no burden to the user from constant background processes. \\

@@

\zbf supports peer-to-peer loading for CSS (via \texttt{link} elements),
Javascript (via \texttt{script} elements), and images (via \texttt{img} elements).
For an existing website to utilize \zbf, the developer simply needs
to make two changes to the DOM elements. \\

The first change is renaming the \texttt{src} or \texttt{href} attribute to
\texttt{data-zf-fallback}. \zbf uses the \texttt{data-zf-fallback} attribute
in order to (1) prevent the browser from automatically fetching the resources,
and (2) provide a URL to be used in the event that the peer-to-peer network
is unable to serve the content. \\

@@

The \zbf architecture consists of several loosely-connected components (see
\Cref{fig:components}). At the highest level, there is a download manager that
provides a reliable download service. It relies on the tracker interface and
the connection manager. The tracker interface facilitates communication with
the central tracker for information about peers and file sizes, and the
connection manager provides an interface for peer-to-peer message transfer. \\

@@

\zbf divides assets into chunks; chunks are individually requested and
sent between peers. We use a standard chunk size of 10240 bytes in our
implementation; preliminary tests showed this chunk size to be reasonable.
When a client asks for a resource, the download manager for that client
determines the number of chunks for that resource from the resource's total size.
The download manager then evenly distributes requests for these chunks
among the peers with the resource. \\
Requests for chunks time out on a per-chunk basis. We track the time \zbf
last sent a request for each chunk; if this time exceeds a cutoff, we randomly
choose another peer with the resource and send the chunk request to that
peer. We periodically retrieve an updated peers list for this resource
from the tracker. \zbf uses exponential backoff when sending chunk requests
so we don't flood peers with requests as a result of slow network connectivity.

@@

\subsection{Per-chunk hash validation}
As of right now, \zbf verifies the integrity of the downloaded resource once all
chunks have been retrieved and joined. In normal circumstances where all chunks
successfully download, this may not prove to be an issue. However, waiting until
all chunks are downloaded and combined to verify the file means that if a single
chunk had been corrupted or compromised, all chunks for the file would need to be
downloaded, combined, and verified again. \\

>>>>

\section{Introduction}
It is common for personal blogs and other small websites to gain sudden attention
on large, high-traffic websites such as reddit. Since these websites usually
experience much smaller traffic loads, the hardware devoted to hosting them
is typically not powerful enough to cope with this large influx of content requests.
These sudden, unexpected bursts of traffic often result in websites loading at
extremely slow speeds, or not loading at all, and is colloquially known as the
``reddit hug of death'' or the ``reddit effect.''

Typical means for dealing with this situation involve utilizing Content
Delivery Networks (CDNs), but these are expensive, especially for websites
which only experience such high loads on an occasional basis. An ideal solution
would be a lightweight means to mimic the benefits of an ordinary CDN, which is
typically backed by a robust network of machines.

In this paper, we present \zbf, a peer-to-peer CDN. \zbf provides an easy way
for developers to distribute content to clients via a peer-to-peer network,
rather than directly from the central server that hosts the content. \zbf
is comprised of a server-side component and a client-side component. The
centralized, server-side component both tracks resource propagation metadata
and acts as an assist for opening peer-to-peer data channel connections. The
lightweight client-side component requests resources from peers and distributes
resources in response to peer requests.

\zbf's design is based on the BitTorrent protocol~\cite{cohen:bittorrent}, by which
clients requesting content attempt to receive chunks of data from other
clients, rather than retrieving the entire file from a central server. As
with BitTorrent trackers, any developer could host their own tracker and service
it to connect peers requesting a resource with peers distributing the resource.

The \zbf client-side code runs purely in the browser, and is completely transparent
to the user. The user does not have to install any application on their
computer to obtain desired resources peer-to-peer. As a result, the \zbf client
code only runs when a user is currently visiting the website, therefore adding
no burden to the user from constant background processes.

@@

\zbf supports peer-to-peer loading for CSS (via \texttt{link} elements),
Javascript (via \texttt{script} elements), and images (via \texttt{img} elements).
For an existing website to utilize \zbf, the developer simply needs
to make two changes to the DOM elements.

The first change is renaming the \texttt{src} or \texttt{href} attribute to
\texttt{data-zf-fallback}. \zbf uses the \texttt{data-zf-fallback} attribute
in order to (1) prevent the browser from automatically fetching the resources,
and (2) provide a URL to be used in the event that the peer-to-peer network
is unable to serve the content.

@@

The \zbf architecture consists of several loosely-connected components (see
\Cref{fig:components}). At the highest level, there is a download manager that
provides a reliable download service. It relies on the tracker interface and
the connection manager. The tracker interface facilitates communication with
the central tracker for information about peers and file sizes, and the
connection manager provides an interface for peer-to-peer message transfer.

@@

\zbf divides assets into chunks; chunks are individually requested and
sent between peers. We use a standard chunk size of 10240 bytes in our
implementation; preliminary tests showed this chunk size to be reasonable.
When a client asks for a resource, the download manager for that client
determines the number of chunks for that resource from the resource's total size.
The download manager then evenly distributes requests for these chunks
among the peers with the resource.

Requests for chunks time out on a per-chunk basis. We track the time \zbf
last sent a request for each chunk; if this time exceeds a cutoff, we randomly
choose another peer with the resource and send the chunk request to that
peer. We periodically retrieve an updated peers list for this resource
from the tracker. \zbf uses exponential backoff when sending chunk requests
so we don't flood peers with requests as a result of slow network connectivity.

@@

\subsection{Per-chunk hash validation}
As of right now, \zbf verifies the integrity of the downloaded resource once all
chunks have been retrieved and joined. In normal circumstances where all chunks
successfully download, this may not prove to be an issue. However, waiting until
all chunks are downloaded and combined to verify the file means that if a single
chunk had been corrupted or compromised, all chunks for the file would need to be
downloaded, combined, and verified again.
